Typed Functional Genetic Programming

### 2013-06-25 tex/thesis.tex
[tex] Our approach to solving Inhabitation tree and stuff...

\newcommand{\Lets}{Let us }
\newcommand{\lterm}{$\lambda$-term\xspace}
\newcommand{\lterms}{$\lambda$-terms\xspace}

@@

\newcommand{\EA}{EA } % TODO nahradit správnym "evoluťionar algorithms"

@@

In \EA there is plenty of options for selection mechanisms 
for us to choose from. Again we will describe mechanism Koza
used in his first book on GP. It is \textit{Roulette selection}.
It uses fitness value of each individual in straightforward way to determine probability of selecting this individual.\\

@@

Then $p_{i}$ probability of selection of individual $i$ is computed
as follows:\\

$p_{i} = \dfrac{ f_{i}  }{ \Sigma_{j=1}^{popSize} f_{j} } $

@@

Now we will resolve the child nodes of the root node.

There are two cases of $\sigma$ (recall \ref{deftype}): 
\begin{description}
	\item[Atomic type] 
		$\sigma = \alpha $ where $\alpha \in A$. 
	\item[Function type] 
		$\sigma = \tau_1 \rightarrow \dots \rightarrow \tau_n \rightarrow \alpha$
		where $n \geq 1, \alpha \in A$.
\end{description}

@@

~\\
\textbf{TODO} 
\begin{itemize}
\item EXAMPLES of tree representations of \lterms  
\item TALK (more?) ABOUT "Barendregt-like" subsection \ref{barlike}\\
		Things about $\beta\eta$ normal form, etc.    
\end{itemize}

\subsection{Our approach to \textit{solving} Inhabitation machine}

@@

\subsection{Inhabitation Machine}
\textbf{TODO} 
\begin{itemize}
\item DESCRIBE Inhabitation Machine...
\end{itemize}

\section{Roadmap}
	\section{Conversion to SKI combinators}

\chapter{ Designed system }	
	\section{Top level view}
		\subsection{Comments about main source files}
			\subsubsection{ Eva.hs }
			\subsubsection{ GP\_{}Core.hs }
	\section{Term generating}
		\subsection{A* algorithm}
	\section{Crossover}
		\subsection{Finding same types}
		\subsection{Two basic options}
		Resolve problems with free variables or avoid variables completely.

@@

@@

>>>>

\newcommand{\Lets}{Let us }
\newcommand{\lterm}{$\lambda$-term\xspace}
\newcommand{\lterms}{$\lambda$-terms\xspace}
\newcommand{\lhead}{$\lambda$-head\xspace}
\newcommand{\lheads}{$\lambda$-heads\xspace}

@@

\newcommand{\EA}{EA\xspace} % TODO nahradit správnym "evoluťionar algorithms"

@@

In \EA there is plenty of options for selection mechanisms 
for us to choose from. Again we will describe mechanism Koza
used in his first book on GP. It is the \textit{Roulette selection}.
It uses fitness value of each individual in straightforward way to determine probability of selecting this individual.\\

@@

Then $p_{i}$ probability of selection of individual $i$ is computed
as follows:

$$ p_{i} = \dfrac{ f_{i}  }{ \sum\limits_{j=1}^{popSize}{f_{j} }  } $$

@@

\begin{samepage}
Now we will resolve the child nodes of the root node.
There are two cases of $\sigma$ (recall \ref{deftype}): 
\begin{description}
	\item[Atomic type] 
		$\sigma = \alpha $ where $\alpha \in A$. 
	\item[Function type] 
		$\sigma = \tau_1 \rightarrow \dots \rightarrow \tau_n \rightarrow \alpha$
		where $n \geq 1, \alpha \in A$.
\end{description}
\end{samepage}

@@

~\\
\textbf{TODO} 
\begin{itemize}
\item EXAMPLES of tree representations of \lterms  
\item TALK (more?) ABOUT "Barendregt-like" subsection \ref{barlike}\\
		Things about $\beta\eta$ normal form, etc.   
\item DESCRIBE Inhabitation Machine... 
\end{itemize}

\subsection{Our approach to \textit{solving} Inhabitation tree}

The main design choice behind our approach to solving inhabitation trees
is ability to be variable enough to enable choice between 
\textit{systematic} way of generating terms 
and \textit{classical-GP-like} way of generating terms 
by choice of simple search strategy.\\

\Lets explain what is meant by \textit{systematic} and \textit{classical-GP-like}. \\

\textit{Systematic} way of solving inhabitation tree corresponds to
generating terms in order from smallest to largest in number of symbols and \lheads.
That means minimizing number of and-nodes in and-or-tree view of point on inhabitation tree.
But since inhabitation tree is a special kind of and-or-tree with alternating layers of 
and-nodes (symbols and \lheads) and or-nodes (types) it is also minimizing number of 
size of whole inhabitation/and-or tree. \\

\textit{Classical-GP-like} ... \textbf{TODO}

@@

A* is a general informed search algorithm used for finding shortest path in a state space.
According to \cite{AIAMA} A* is the most widely known form of best-first search.

\section{Conversion to SKI combinators}

\chapter{ Designed system }	
	\section{Top level view}
		\subsection{Comments about main source files}
			\subsubsection{ Eva.hs }
			\subsubsection{ GP\_{}Core.hs }
	\section{Term generating}
	\section{Crossover}
		\subsection{Finding same types}
		\subsection{Two basic options}
		Resolve problems with free variables or avoid variables completely.

@@

\chapter{Ideas yet not implemented}

\section{Roadmap}
\section{Tree ants}
\section{[Propojení těch dvou barandrechtskejch odvozovacích pravidel do jedinýho]}
\section{[Chytřejší heuristika pro A* která si to předpočítá na $\overline{\Gamma}$ ]}

@@

\bibitem{AIAMA}

	Stuart J. Russell, Peter Norvig,
	\emph{Artificial Intelligence: A Modern Approach}.
	Pearson Education,
	2003.
